Theories of deliberated judgment

### 2022-08-06 simple.tex
Started def DC with P as pref

\subsection{Deliberated choice}
The deliberated choice of $i$ given the exposure protocol $(I, \allargs, {\allleadsto})$ is denoted $\iprops$ and is a strict subset of $\allprops$, with the semantics that $\iprops = \set{\prop}$ iff $\prop$ is considered by $i$ as the best option among the proposed set $\allprops$, after deliberation, given the exposure protocol. In other words, if $\iprops = \set{\phi}$, the individual considers $\phi$ strictly better than $\nprop$, after deliberation (and conversely for $\iprops = \set{¬\phi}$); and if $\iprops = \emptyset$, the deliberated judgment of $i$ considers neither $\phi$ nor $¬\phi$ as strictly better than the alternative. This latter possibility covers both the situation of indifference between both options (in the sense of being evaluated by $i$ as being exactly equally worth), which will be further developed in \cref{sec:multiple}, or the situation that $\phi$ is neither deliberately strictly better than, exactly equivalent to or strictly worst than $\nprop$.

@@

The formal definition of $\iprops$ given $(I, \allargs, {\allleadsto})$ requires to define the notion of decisive argument.

@@

Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \nileadsto \nprop$; equivalently, iff $\forall \hist \in \allhist \suchthat \ar \in \histend: {\leadsto}(i, \hist) = \set{\prop}$.
When $\ar \ileadstost \prop$, $\ar$ is said to be a decisive argument for $\prop$ from $i$’s point of view (or just a decisive argument, for short). 
The deliberated judgment of $i$ is then considered to contain the set of propositions supported by decisive arguments.
\begin{axiom}[Decisive arguments define deliberated judgments]
	\label{ax:decisive}
	$\forall i \in I, \prop \in \allprops: 
		\prop \in \iprops ⇔ [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop].$
\end{axiom}

>>>>

\subsection{Deliberated choice}
The deliberated choice of $i$ given the exposure protocol $(I, \allargs, {\allleadsto})$ is denoted $p_i \in P$, with the semantics that $p_i$ represents the preference of $i$ over the proposed set of two acts, after deliberation, given the exposure protocol. In other words, if $p_i = \phi$, the individual considers the first act strictly better than the second one, after deliberation (and conversely for $p_i = ¬\phi$); and if $p_i = 0$, the deliberated choice of $i$ considers neither no act as strictly better than the alternative. This latter possibility covers both the situation of indifference between both options (in the sense of being evaluated by $i$ as being exactly equally worth), which will be further developed in \cref{sec:multiple}, or the situation that no act is deliberately strictly better than the other one and that they are also not deliberately exactly equivalent to each other.
\footnote{It should be clear that $P$ as used as the codomain of ${\leadsto}$ and as the set of possible values of $p_i$ denote different entities. The letter is reused simply to reduce notations. The value ${\leadsto}(i, \alpha) \in P$ designates the directly observed choice of $i$ whereas the value $p_i \in P$ designates the non directly observable deliberated choice of $i$%; furthermore, $0$ in particular may acquire a very different meaning as the value ${\leadsto}(i, \alpha)$ than as the value $p_i = 0$
.}

@@

The formal definition of $p_i$ given $(I, \allargs, {\allleadsto})$ requires to define the notion of decisive argument.

@@

Given $i \in I, p \in P, \ar \in \allargs$, define $\ar \ileadstost p$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadsto p$.
When $\ar \ileadstost p$, $\ar$ is said to be a decisive argument for $\prop$ from $i$’s point of view given the exposure protocol. 
The deliberated judgment of $i$ is then considered as the set of propositions supported by decisive arguments.
\begin{axiom}[Decisive arguments define deliberated judgments]
	\label{ax:decisive}
	$\forall i \in I, p \in P: 
		p \in P_i ⇔ [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop].$
\end{axiom}
